sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-29 doc/paper.Rmd
Force add figs

```{r diagram, fig.cap="(ref:diagram-fig)"}
dir.create("figs", showWarnings = FALSE)
f <- here::here("figs", "diagram-2021-12-10.pdf")
if (!file.exists(f)) {
  download.file("https://www.dropbox.com/s/lvoem3ahwkftzjy/diagram-2021-12-10.pdf?dl=1", 
    destfile = f)
}
knitr::include_graphics(f)
```

@@

```{r pcod-fig, fig.cap="(ref:pcod-fig-cap)", out.width="5.2in", fig.align='center'}
pcodfig <- here::here("figs", "pcod-fig.pdf")
if (!file.exists(pcodfig)) {
  download.file("https://www.dropbox.com/s/s8kl4u49p27qqhy/pcod-fig.pdf?dl=1", 
    destfile = pcodfig)
}
knitr::include_graphics(pcodfig)
```

@@

```{r owl-nao, fig.cap="(ref:owl-nao-fig)", out.width="4.1in", fig.align='center'}
owl <- here::here("figs", "owl-nao-effect-2021-12-22.pdf")
if (!file.exists(owl)) {
  download.file("https://www.dropbox.com/sh/p5ydljdycaw9x6n/AAAlaKQArhqP9IHvUSxEq_qWa/owl-nao-effect-2021-12-22.pdf?dl=0", 
    destfile = owl)
}
knitr::include_graphics(owl)
```

>>>>

```{r diagram, fig.cap="(ref:diagram-fig)"}
dir.create("figs", showWarnings = FALSE)
f <- here::here("figs", "diagram.pdf")
knitr::include_graphics(f)
```

@@

```{r pcod-fig, fig.cap="(ref:pcod-fig-cap)", out.width="5.2in", fig.align='center'}
pcodfig <- here::here("figs", "pcod-fig2.pdf")
knitr::include_graphics(pcodfig)
```

@@

```{r owl-nao, fig.cap="(ref:owl-nao-fig)", out.width="4.1in", fig.align='center'}
owl <- here::here("figs", "owl-nao-effect.png")
knitr::include_graphics(owl)
```
